### 2021-04-09 paper.Rmd
Small additions to the discussion.

This review highlights the history of the grand tour and its modern extensions for the visualization of high dimensional numerical data. A rich ecosystem of tour methods are being actively developed and are finding applications in a broad range of areas. Tours are being combined with interactive graphics to assist with cluster analysis (the spinifex and liminal packages), to understand higher dimensional space and find lower dimensional structure (the sage algorithm, slicing and sectioning) <!-- Ursula can you edit this? -->, and to diagnose optimization procedures for projection pursuit (ferrn).

There are many possible future directions for tour research, one big limitation
of the current software ecosystem is that analysts are no longer able to perform interactions that were possible in software packages from the 80s and 90s. An interactive graphics system that integrated the tour methodology directly would be a big step forward. <!-- Ursula to add sentence on Catherine Hurley's work and other aspects -->

>>>>

This review highlights the history of the grand tour and its modern extensions for the visualization of high dimensional numerical data. A rich ecosystem of tour methods are being actively developed and are finding applications in a broad range of areas. Tours are being combined with interactive graphics to assist with cluster analysis (the spinifex and liminal packages), displays of projected data are augmented to allow the identification of local structures (the sage algorithm, slicing and section pursuit), and  new visualizations based on tour methods are used to better diagnose optimization procedures for projection pursuit (ferrn).

There are many possible future directions for tour research, one big limitation
of the current software ecosystem is that analysts are no longer able to perform interactions that were possible in software packages from the 80s and 90s. An interactive graphics system that integrated the tour methodology directly would be a big step forward. Such an interface could also be combined with methods for conditional model visualization, for example as implemented in the condviz package [@JSSv081i05], allowing the visual exploration of multivariate fitted models.
